User Guide for KvApp

### 2022-04-01 KvApp_guide.Rmd
User manual

---
title: "User Guide for KvApp"
author: "Haedong Kim"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

## Examples

### Example 1: 4.5-sec Data

example with 9 voltage steps rather than the full data.

### Example 2: 25-sec Data

example with 25-sec data

>>>>

---
title: "User Guide for KvApp"
author: "Haedong Kim"
date: "`r Sys.Date()`"
output: word_document
---

@@

## Example

This section provides an example of using the application. A data set will be used having voltage steps from -30 to 50 mV lasting 4.5 s from holding voltage -70 mV. The data is saved in the provided file, `15o27010.xlsx`. First update the protocol accordingly and upload the data as in Figure 7.

![Data upload.](KvApp_guide_img/exp1-1.png)

Discrepancies between the model prediction and exerrmental I~Ksum~ traces can be observed in the bottom right figure. To calibrate the models according to the data, click the Run Calibration button. It will change to a progress bar as in Figure 8.

![Run calibration.](KvApp_guide_img/ex1-2.png)

Once the calibration is completed, the model outputs and kinetics are updated as in Figure 9.

![Calibration results.](KvApp_guide_img/ex1-3.png)
